Protein-intrinsic properties and epigenetic effects regulate pioneer-factor binding and function

### 2023-03-21 manuscript/manuscript_sections/_05_Methods.qmd
add GEO accession to methods

Sequencing data have been deposited in the Gene Expresion Omnibus under accession GSEXXXX.
All analysis code is available on GitHub: https://github.com/tjgibson/S2_pioneers_manuscript.

>>>>

Sequencing data have been deposited in the Gene Expresion Omnibus under accession GSE227884
All analysis code is available on GitHub: https://github.com/tjgibson/S2_pioneers_manuscript.
